From physical principles to ???

### 2016-05-09 2015CompleteDerivation/completeDerivation.tex
First full pass at justification for integration

\begin{defn}\label{integration}
	The state space $\mathcal{S}$ for the particles of a homogeneous classical material is endowed with a measure $\mu$. The state space $\mathcal{C}$ is isomorphic to the space of continuous functions that are integrable over any subset of $\mathcal{S}$. That is: $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$.
\end{defn}

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each open set $U \subseteq \mathcal{S}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. Let $U_1, U_2$ two disjoint sets, then $\Lambda_U = \Lambda_{U_1} + \Lambda_{U_2}$ as the material found in $U$ must be either in $U_1$ or $U_2$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decrease the amount of material by a factor. $\Lambda_U$ is positive. If the value of distribution at each particle state is positive then the total amount of material is positive.

	We claim that $\mathcal{S}$ is endowed with a Borel measure $\mu$. $\mathcal{S}$ is locally compact as it is a manifold. At each point there exists an compact open a neighborhood $U$. $U$ with the subspace topology is a compact Hausdorff space on which is defined a positive linear function $\Lambda_U$ on the linear vector space $\mathcal{C}$ isomorphic to the space of continuous compactly supported real valued functions defined on $U$. For the Riesz representation theorem for linear functionals, there exists a unique Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. $\Lambda_U$ is the sum for disjoint subsets, therefore $\Lambda_V (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$ for any open set $V \supseteq U$. The measure is unique in the family of all functionals $\Lambda_U$. $\Lambda_U(\mathcal{c})$ is finite for any open, therefore $\Lambda_{\mathcal{S}} (\mathcal{c}) = \int_{\mathcal{S}} \rho_{\mathcal{c}} d \mu$. The measure is unique on the whole space.
\end{justification}

>>>>

\begin{defn}\label{integration}
	The state space $\mathcal{S}$ for the particles of a homogeneous classical material is endowed with a Borel measure $\mu$. The state space $\mathcal{C}$ is isomorphic to the space of continuous functions that are integrable over any subset of $\mathcal{S}$. That is: $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$.
\end{defn}

\begin{justification}
	We claim there exists a positive linear functional $\Lambda_U : \mathcal{C} \rightarrow \mathbbm{R}$ for each open set $U \subseteq \mathcal{S}$. Let $\Lambda_{U} : \mathcal{C} \rightarrow \mathbbm{R}$ the functional that returns the amount of material in $\mathcal{c}$ compatible with the outcome associated with the open set $U \subseteq \mathcal{S}$. $\Lambda_U$ is linear. $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$ as it has to be consistent with the operations of composing states and increasing/decrease the amount of material by a factor. $\Lambda_U$ is positive. If the value of the distribution for each particle state is positive then the total amount of material is positive.

	We claim that $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$. Let $U \subseteq \mathcal{S}$ be the open set of particle states associated with an outcome. Let $\mathcal{c} \in \mathcal{S}$ a composite state. As physically we always work with finite quantities, the amount of material of $\mathcal{c}$ associated with the outcome $U$ must be finite. $|\Lambda_{U}(\mathcal{c})| < \infty$.

	We claim that $\Lambda_{U_1} + \Lambda_{U_2} = \Lambda_{U_1 \cup U_2} + \Lambda_{U_1 \cap U_2}$ $\forall $ open $U_1, U_2 \in \mathcal{S}$. Let $U_1, U_2 \in \mathcal{S}$ be the open sets of particles states associated with two outcomes. Suppose $U_1 \cap U_2 = 0$, $\Lambda_{U_1 \cup U_2} = \Lambda_{U_1} + \Lambda_{U_2}$ as the material found in $U_1 \cup U_2$ must be either in $U_1$ or $U_2$. Suppose $U_1 \cap U_2 \neq 0$, $\Lambda_{U_1 \cup U_2} = \Lambda_{U_1} + \Lambda_{U_2} - \Lambda_{U_1 \cap U_2}$ as the sum of the material associated with each outcome will double count the intersection.

	We claim that each $U \subseteq \mathcal{S}$ is endowed with a Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$. $\mathcal{S}$ is locally compact as it is a manifold. At each point there exists a compact open a neighborhood $U$. $U$ with the subspace topology is a compact Hausdorff space on which is defined a positive linear function $\Lambda_U$ on the linear vector space $\mathcal{C}$ isomorphic to the space of continuous compactly supported real valued functions defined on $U$. For the Riesz representation theorem for linear functionals, there exists a unique Borel measure $\mu_U$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U$.

	We claim that $\mathcal{S}$ is endowed with a unique Borel measure $\mu$ such that $\Lambda_U (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu$. Let $V \subseteq \mathcal{S}$ an open set. Let $U \subseteq V$ not necessarily open. As $\rho_{\mathcal{c}}$ is continuous, $\int_{U} \rho_{\mathcal{c}} d \mu_V = \int_{\mathrm{Int} U} \rho_{\mathcal{c}} d \mu_V$. We extend $\Lambda_U \equiv \Lambda_{\mathrm{Int}U}$ to all sets. We have $\Lambda_V (\mathcal{c}) = \int_V \rho_{\mathcal{c}} d \mu_V = \int_U \rho_{\mathcal{c}} d \mu_V + \int_{V\backslash U} \rho_{\mathcal{c}} d \mu_V$. We also have $\Lambda_V (\mathcal{c}) = \Lambda_U (\mathcal{c}) + \Lambda_{V\backslash U} (\mathcal{c}) = \int_U \rho_{\mathcal{c}} d \mu_U + \int_{\mathrm{Int} V \backslash U} \rho_{\mathcal{c}} d \mu_{\mathrm{Int} V \backslash U} $. As the two have to be equal for all $U, V, \rho_{\mathcal{c}}$, we must have $\int_{U} \rho_{\mathcal{c}} d \mu_U = \int_{U} \rho_{\mathcal{c}} d \mu_V$. Therefore $d\mu$ is unique for each open set in the family of all functionals. As $\mathcal{S}$ is locally compact, we can find a cover of compact sets. $\Lambda_{\mathcal{S}}(\mathcal{c})$ will be the sum of contributions of the elements of the cover and their intersections. As $\Lambda_U$ is always finite, $\Lambda_{\mathcal{S}}$ is a finite sum of finite contributions. Therefore we have  $\Lambda_{\mathcal{S}} (\mathcal{c}) = \int_{\mathcal{S}} \rho_{\mathcal{c}} d \mu$. The measure is unique on the whole space.

	We claim $\mathcal{C} \cong C(\mathcal{S}) \cap  L^1_{ew}(\mathcal{S}, \mu)$ where $L^1_{ew}(\mathcal{S}, \mu) = \{ \rho : \mathcal{S} \rightarrow \mathbbm{R} \; | \;\; |\int_{U} \rho d\mu| < \infty \; \forall U \subseteq \mathcal{S}\}$. As per \ref{classical_vector space} $\mathcal{C}$, is isomorphic to a subspace $G \subseteq C(\mathcal{S})$ as a vector space over $\mathbbm{R}$. As $|\Lambda_{U}(\mathcal{c})| < \infty \; \forall \mathcal{c} \in \mathcal{C} \; \forall U \subseteq \mathcal{S}$, then $G \subseteq L^1_{ew}(\mathcal{S}, \mu)$. TODO: can we prove mathematically that we have to span the whole space to be closed under linear combinations? 
\end{justification}
